cardinalR: Generating interesting high-dimensional data structures

### 2025-10-06 paper-cardinalR.Rmd
Added application for Trefoil knots
Added application for cone

@@

>>>>

Cone-shaped structures appear in particle dispersions, light beams, and tapering processes, where spread decreases along one axis. They are also used to benchmark clustering and dimensionality reduction methods [@hadsell2006].

@@

The trefoil knot appears in molecular biology (DNA/protein knotting), fluid dynamics (knotted vortices), and physics (topological phases), making it a useful benchmark for testing whether dimension reduction preserves global loops and topology [@witten1985; @arsuaga2002].

### 2025-10-06 paper-cardinalR.tex
Added application for Trefoil knots
Added application for cone

@@

>>>>

Cone-shaped structures appear in particle dispersions, light beams, and tapering processes, where spread decreases along one axis. They are also used to benchmark clustering and dimensionality reduction methods \citep{hadsell2006}.

@@

The trefoil knot appears in molecular biology (DNA/protein knotting), fluid dynamics (knotted vortices), and physics (topological phases), making it a useful benchmark for testing whether dimension reduction preserves global loops and topology \citep{witten1985, arsuaga2002}.
